Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-29 Ben_Manuscripts/Paper1/Outline.tex
Outlining methods

>>>>

  \section*{Methods}

  HII monomers were parameterized using the Generalized AMBER Forcefield
  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006}
  provided with AmberTools16 \cite{case_ambertools16_2016}. Atomic charges were
  assigned using tools from Openeye Scientific Software. All molecular dynamics 
  simulations were run using the latest version of Gromacs 2016. 
  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

  An ensemble of characteristic, low-energy vacuum monomer configurations
  were constructed by applying a simulated annealing process to a
  parameterized monomer.
  \begin{itemize}
    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
    \item A low energy configuration was pulled from the trajectory 
    and charges were reassigned using the am1bccsym method of molcharge
    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
    \item Using the new charges, the monomer system was annealed again and monomer
    configurations were pulled from the trajectory to be used for full
    system construction (Figure~\ref{fig:python}a).
  \end{itemize}

  The timescale for self assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic
  simulation, calling for a more efficient way to build the system. 
  \begin{itemize}
    \item Previous work has shown a coarse grain model self assemble into
    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
    \item We attempted atomistic self-assembly by packing monomers into a box 
    using Packmol \cite{martinez_packmol:_2009}.
    \item Simulations of greater than 100 ns show no indicators of progress 
    towards an ordered system.
    \item To bypass the slow self-assembly process, python scripts are used
    to assemble monomers into a structure close to the expected equilibrium 
    configuration (Figure~\ref{fig:python}).
    \item A short, restrained equilibration, followed by NPT simulations 
    between 400 and 500 ns, allows the initial configuration to relax into
    an equilibrium configuration.
    \item Our logic for choosing a starting configuration and the details 
    of the equilibration schemes are presented below.
  \end{itemize}

  \begin{figure}[H]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
  \end{figure}

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended 
  periodically.
  \begin{itemize}
    \item Each pore is made of twenty stacked monomer layers with periodic 
    continuity in the z direction, avoiding any edge effects and creating an 
    infinite length pore ideal for studying transport.
    \item A small number of layers is preferred in order to reduce computational
    cost and to allow us to look at longer timescales.
    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
    This point will be explained in more detail later.
  \end{itemize}

  We chose initial guesses for the remaining structural parameters based on 
  experimental data and treated them as variables during model development.
  \begin{itemize}
    \item The distance between pores was based on experimental SAXS data for
    this system \cite{feng_thin_2016}.
    \item The model's pores are spaced 4.5 nm apart initially, \approx 10 \% larger
    than the experimental value in order to reduce unintended repulsions 
    resulting from a tightly packed initial configuration.
    \item The layer spacing is based on experimental 2D WAXS data.
    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom apart.
    \item It has been hypothesized that the features are a result of pi-pi
    interactions between stacked aromatic rings \cite{feng_scalable_2014}.

  An equilibration scheme with position restraints placed on aromatic rings
  prevents unrealistic jumps during early equilibration steps.

  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.

  \begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

  Ionic conductivity was calculated using two different methods for
  robustness.

  Using an equilibrated structure, a crosslinking procedure was performed
  in order to better parallel synthetic procedures.
